---
title: "exercise1"
author: "Marazzini, Zaccaro"
date: "26/11/2022"
output: html_document
---

# Report - Correlation between democracy and city size

## Introduction

*Is democracy perceived as more important in big cities or in small cities?*

This is the question that drove our research.

Since in big cities there are more individuals, it's more likely there are more people that want to express their own opinion. For this reason, we hypothise in big cities democracy is perceived as more important.

## Method

To do this research we used a data set named ZA7505_v3_0\_0 from GESIS. We analyzed two variables: size_5c, which reports the size for the cities, and E235, which corresponds to the importance of democracy.

The first variable assembles the cities in five groups according to their size:

\- 1: under 5000

\- 2: 5000-20000

\- 3: 20000-100000

\- 4: 100000-500000

\- 5: 500000 and more

The second variable is a Liker scale to express the importance of democracy, where 1 stands for "not at all" and 10 means "absolutely important".

To start our analysis we created a frequency table deleting the values of no interest, such as the "missing values" and the "not answered" :

```{r}
librabry(rio)
import("ZA7505_v3-0-0.dta") 

dataset <- ZA7505_v3_0_0
with(dataset,table(ZA7505_v3_0_0$E235, ZA7505_v3_0_0$size_5c, exclude= -5:-1))
```

## Regression Analysis

To establish if there is an association between the two variables, we run a Regression Analysis, establishing the following hypothesis:

\- H0: statitically independence - Ha: statistically dependence

```{r}
library(tidyverse)
cor <- lm(size_5c ~ E235,
          data = dataset)

summary(cor)
```

Looking at the results, we can notice a very small P-value, whereas the t-value is huge. From this we can reject the null hypothesis and state that there is an association between the importance of democracy and the size of the cities. Yet, this correlation is weak, as the R-squared value is nearly zero.

### Graphical Visualization

To prove the correlation, we visualized the results in a graph:

```{r}
ggplot(dataset, aes(x = size_5c, y = E235)) +
  geom_smooth(method = "lm", se = T) +
  ylab("Democracy index") +
  xlab("City Size")
  theme_light()
```
The graph confirms the dependence of the variables, since there is not a flat line but there is a slope. 
We can notice that the variables are inversely proportional: the bigger the city is, the less democracy is perceive as important.

## Conclusion
According to our results, it is clear that the importance of democracy and the size of the cities are correlated, even if the strength of the association is weak. 
In particular, the dependence is inversely proportional: in fact, as the city size increases, the level of the importance of democracy decreases. 

## Discussion
